A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-04-20 article.tex
引言部分的修改（未完成）

By the end of 2017, China's installed capacity of generating units was 1 billion 780 million kilowatts, of which coal-fired units accounted for more than 50\% of the total installed capacity of the country. 
In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis} ~\cite{2018}.
Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{2017}. 
Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design. Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
 Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
 The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
 Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.

Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.

@@

Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.

>>>>

By the end of 2017, China's installed capacity of generating units was 1,780 million kW, of which coal-fired units accounted for more than 50\% of the total installed capacity~\cite{2018}, and coal–fired power generation accounts for almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively, in China~\cite{Zhang2010Analysis}.
In 2016, Chinese steam coal price increased by over 60\%~\cite{2017} which caused a great burden on coal-fired power generation enterprises. 
Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design.

% Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
% The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
% According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
%  The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
%  Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
%  The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
%  Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

 为了能够提高热电厂的循环效率，研究人员不断对火电厂系统进行改进优化。
 Sven Kjaer et al.~\cite{Kjaer2010A} considered that those investigations can be grouped along three side tracks, i.e. the temperature track, which employs higher live steam parameters such as 30-35 MPa, above 700$^\circ$C in the future~\cite{Bugge2014High}, the component track, which improves the efficiency of key equipment such as boiler~\cite{Rosen2008Improving} and turbine~\cite{Zhang2016Optimization}, and the Carnot track, which makes efforts to reduce the defection of the real cycle of the power plant~\cite{Liu2018}.

对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：

二次再热也已经作为一种有效提高系统效率的方式被深入研究并进行深入分析：

@@

% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.

% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.

现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。而通过火用分析，热力系统中锅炉损失占总用损失的70%，空预器的损失和整个回热系统的损失相当。
通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
这一点对于二次再热系统尤为重要，随着近年来二次再热机组在世界范围研究和投入使用，其高效收到的广泛的认可，但是由于再热后抽汽的过热度提高，导致抽汽和给水温度不匹配造成的用损失也更加显著。
所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。

% Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.
